\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-12-23 overview.tex
update

The goal of our work is to detect distributed system bugs \emph{before} they reach production. Distributed systems typically consist of multiple components that interact with each other via \emph{message passing}. If these messages---or unexpected failures and timeouts---are not handled properly, they can lead to subtle bugs. To expose these bugs, we use \psharp~\cite{deligiannis2015psharp}, an extension of the \csharp language that provides: (i) language support for \emph{modeling} the environment of distributed systems written in .NET; and (ii) a \emph{systematic testing engine} that can explore interleavings between \emph{distributed events}, such as the nondeterministic order of message deliveries, failures and timeouts.

Modeling using \psharp involves two core activities. First, the developer must modify the original system so that messages are not sent through the real network, but are instead dispatched using the \psharp \texttt{Send} method. Such modification is typically non-invasive, as it can be performed with dynamic dispatch, a \csharp language feature already used for unit testing. Second, the developer must write a \psharp test harness that nondeterministically triggers various distributed events, such as client requests, failures and timeouts. The purpose of these two modeling activities is to explicitly declare all possible sources of nondeterminism in the distributed system using \psharp.

@@

Due to the highly asynchronous nature of distributed storage systems, the number of possible states that these systems can reach is exponentially large. Tools such as \textsc{MoDist}~\cite{yang2009modist} and dBug~\cite{simsa2011dbug} focus on testing unmodified distributed systems, but this can easily lead to state-space explosion when trying to exhaustively explore the entire state-space of a production-scale system, such as the Azure Storage vNext. On the other hand, techniques such as TLA+~\cite{lamport1994temporal} have successfully verified specifications of distributed systems, but they are unable to verify the actual implementation. In this work, we are proposing a solution between the two extremes: systematically test the implementation of a distributed system component against its modeled by \psharp environment. The benefit of our approach is that it can detect bugs in the \emph{actual} implementation, but it can do so in a much reduced state-space. Testing with our approach does not come for free; developers have to invest effort and time into building a test harness and environment using \psharp. However, we argue that developers already spend significant time in building test suites and testing a distributed system prior to deployment. The \psharp approach augments this effort; by investing time in modeling the environment, it offers dividends by finding more bugs (see \S\ref{sec:eval}).

>>>>

The goal of our work is to detect distributed system bugs \emph{before} they reach production and effect users. Distributed systems typically consist of multiple components that interact with each other via \emph{message passing}. If messages---or unexpected failures and timeouts---are not handled properly, they can lead to subtle bugs. To expose these bugs, we use \psharp~\cite{deligiannis2015psharp}, an extension of the \csharp language that provides: (i) language support for \emph{modeling} the environment of distributed systems written in .NET; and (ii) a \emph{systematic testing engine} that can explore interleavings between \emph{distributed events}, such as the nondeterministic order of message deliveries, client requests, failures and timeouts.

Modeling using \psharp involves two core activities. First, the developer must modify the original system so that messages are not sent through the real network, but are instead dispatched through the \psharp \texttt{Send} method. Such modification does not need to be invasive, as it can be performed using virtual method dispatch, a \csharp language feature widely used for testing. Second, the developer must write a \psharp test harness that nondeterministically triggers distributed events. The purpose of these two activities is to explicitly declare all possible sources of nondeterminism in the distributed system using \psharp.

@@

Due to the highly asynchronous nature of distributed storage systems, the number of possible states that these systems can reach is exponentially large. Tools such as \textsc{MoDist}~\cite{yang2009modist} and dBug~\cite{simsa2011dbug} focus on testing unmodified distributed systems, but this can easily lead to state-space explosion when trying to exhaustively explore the entire state-space of a production-scale distributed storage system, such as the Azure Storage vNext. On the other hand, techniques such as TLA+~\cite{lamport1994temporal} have successfully verified specifications of distributed systems, but they are unable to verify the actual implementation.

In this work, we are proposing a solution between the above two extremes: systematically test the implementation of a distributed system component against its modeled by \psharp environment. The benefit of our approach is that it can detect bugs in the \emph{actual} implementation, but it can do so in a much reduced state-space. Testing with our approach does not come for free; developers have to invest effort and time into building a test harness and environment using \psharp. However, we argue that developers already spend significant time in building test suites and testing a distributed system prior to deployment. The \psharp approach augments this effort; by investing time in modeling the environment, it offers dividends by finding more bugs (see \S\ref{sec:eval}).
